---
title: "Predictors of COVID-19 Deaths in Rwanda"
author: "Muhammed Semakula"
date: '2022-07-07'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```
```{r  echo = FALSE}

deaths<-readxl::read_excel("Covid_Deaths.xlsx")
```
```{r  echo = FALSE}
deaths1<-readxl::read_excel("Vanessa data set.xlsx")
```
```{r  echo = FALSE}
Positive_tests <- readr::read_csv("Positive tests.csv")
```

```{r echo=FALSE}
#table(deaths1$Outcome)

```

```{r deaths2,echo=FALSE}
deaths2 <- dplyr::filter(deaths1,Outcome== "Discharged")
names(deaths2)[2]<- "Names"
```
```{r  echo = FALSE}
names(deaths2)[2]<- "Names"
names(deaths2)[3]<- "Age"
names(deaths2)[4]<- "Gender" 
names(deaths2)[7]<- "District" 
names(deaths2)[8]<- "Comorbidity"
names(deaths2)[10]<- "Vaccination status"
```
```{r,echo=FALSE}
death3<-dplyr::left_join(deaths,deaths2,by="Names", )

```
```{r echo=FALSE}

death3<-deaths[1,]
```

```{r echo=FALSE}
deaths3<-deaths[1:876,]

```
```{r echo=FALSE}
deaths3$Names<-deaths2$Names
deaths3$Age<-deaths2$Age
deaths3$Gender<-deaths2$Gender
deaths3$Comorbidity<-deaths2$Comorbidity
deaths3$District<-deaths2$District
deaths3$`Vaccination status`<- deaths2$`Vaccination status`
```
```{r echo=FALSE}
library("dplyr")
library("tidyr")
```



```{r echo=FALSE}
deaths3$outcome <- 0
deaths$outcome <- 1

```
```{r echo=FALSE}
data_d <-rbind(deaths,deaths3)

```  
  

```{r,echo=FALSE}
# Female= 0,Male=1
data_d$Gender[data_d$Gender=="F"] <- "0"
data_d$Gender[data_d$Gender=="Female"] <- "0"
data_d$Gender[data_d$Gender=="M"] <- "1"
data_d$Gender[data_d$Gender=="Male"] <- "1"

```
```{r,echo=FALSE}
data_d$agecat = data_d$Age 
data_d$agecat[data_d$Age < 20] <- "0"
data_d$agecat[data_d$Age >= 20 & data_d$Age < 30] <- "1"
data_d$agecat[data_d$Age >= 30 & data_d$Age < 40] <- "2"
data_d$agecat[data_d$Age >= 40 & data_d$Age < 50] <- "3"
data_d$agecat[data_d$Age >= 50 & data_d$Age < 60] <- "4"
data_d$agecat[data_d$Age >= 60 & data_d$Age < 70] <- "5"
data_d$agecat[data_d$Age >= 70 & data_d$Age < 80] <- "6"
data_d$agecat[data_d$Age >= 80] <- "7"
```
```{r,echo=FALSE}
data_d$`Dose Number`[data_d$`Dose Number`=="1 Dose"] <- "1"
data_d$`Dose Number`[data_d$`Dose Number`=="Dose 1"] <- "1"
data_d$`Dose Number`[data_d$`Dose Number`=="Dose 1&2"] <- "2"
data_d$`Dose Number`[data_d$`Dose Number`=="Dose 1,2&Booster"] <- "3"
data_d$`Dose Number`[data_d$`Dose Number`=="N/A"] <- "0"

```
```{r,echo=FALSE}
data_d$treat <- data_d$`Treatment protocol`

data_d$treat[data_d$`Treatment protocol`=="treated with usual protocol"] <- "1"
data_d$treat[data_d$`Treatment protocol`=="treated with usual protocol."] <- "1"
data_d$treat[data_d$`Treatment protocol`=="treated with usual protocol. Condition did not improve"] <- "1"
data_d$treat[data_d$`Treatment protocol`=="treated with usual protoco"] <- "1"

data_d$treat[data_d$`Treatment protocol`=="treated with antibiotics, favipiravir and oxygen therapy"] <- "2"
data_d$treat[data_d$`Treatment protocol`=="Antibiotics and oxygen"] <- "3"
data_d$treat[data_d$`Treatment protocol`=="Antibiotics, favipiravir and oxygen therapy"] <- "2"
data_d$treat[data_d$`Treatment protocol`=="treated with oxygen therapy and antibiotics"] <- "2"
data_d$treat[data_d$`Treatment protocol`=="cocktail therapy, and oxygen therapy, later intubated"] <- "4"
data_d$treat[data_d$`Treatment protocol`=="treated with oxygen, Favipiravir, Ivermectin"] <- "5"

data_d$treat[data_d$`Treatment protocol`=="favirpiravir and oxygen therapy and later intubated"] <- "5"
data_d$treat[data_d$`Treatment protocol`=="favipiravir, antibiotics, insulin therapy and oxygen therapy, later intubated "] <- "5"
data_d$treat[data_d$`Treatment protocol`=="favipiravir and oxygen therapy, later intubated"] <- "5"
data_d$treat[data_d$`Treatment protocol`=="favipiravir and oxygen therapy later intubated"] <- "5"
data_d$treat[data_d$`Treatment protocol`=="nebulisation, antibiotics and oxygen"] <- "5"

data_d$treat[data_d$`Treatment protocol`=="treated with antibiotics and oxygen therapy"] <- "0"

data_d$treat[data_d$`Treatment protocol`=="oxygen therapy"] <- "0"

data_d$treat[data_d$`Treatment protocol`=="monoclonal antibodies, antibiotics, Favipiravir, and oxygentherapy"] <- "6"
data_d$treat[data_d$`Treatment protocol`=="monoclonal antibodies, antibiotics, and oxygen"] <- "6"

data_d$treat[data_d$`Treatment protocol`=="favipiravir and oxygen therapy"] <- "2"
data_d$treat[data_d$`Treatment protocol`=="favipiravir and mechanical ventilation"] <- "5"
data_d$treat[data_d$`Treatment protocol`=="favipiravir and oxygen therapy including intubation"] <- "5"
data_d$treat[data_d$`Treatment protocol`=="hemodialysis"] <- "7"
data_d$treat[data_d$`Treatment protocol`=="oxygen, antibiotics, favipiravir"] <- "2"
data_d$treat[data_d$`Treatment protocol`=="favipiravir, transfusions and oxygen therapy"] <- "2"
data_d$treat[data_d$`Treatment protocol`=="nebulization and antibiotics"] <- "2"

data_d$treat[data_d$`Treatment protocol`=="oxygen, IV fluids and antibiotics"] <- "1"
data_d$treat[data_d$`Treatment protocol`=="favipiravir, antibiotics, insulin therapy and oxygen therapy, later intubated"] <- "5"

data_d$treat[data_d$`Treatment protocol`=="cocktail therapy, anti HTN drugs, insulin and oxygen therapy, her condition"] <- "4"
data_d$treat[data_d$`Treatment protocol`=="No information"] <- NA
data_d$treat[data_d$`Treatment protocol`=="bedridden for two years and was placed under palliative care"] <- "0"
data_d$treat[data_d$`Treatment protocol`=="treated for his existing conditions and with oxygen therapy"] <- "1"
data_d$treat[data_d$`Treatment protocol`=="treated with antibiotics, favipiravir and oxygen therapy, later intubated"] <- "5"

data_d$treat[data_d$`Treatment protocol`=="treated with antibiotics, oxygen therapy and covid-19 cocktail therapy"] <- "4"
data_d$treat[data_d$`Treatment protocol`=="He was stable and placed in homebased care"] <- "-1"


data_d$treat[data_d$`Treatment protocol`=="placed in homebased care. She developed severed respiratory distress while at home"] <- "-1"


data_d$treat[data_d$`Treatment protocol`=="child were discharged on 25.06 to continue treatment in HBC"] <- "-1"

data_d$treat[data_d$`Treatment protocol`=="followed at CHUK for lower urinary tract symptoms, prostatectomy for benign prostatic hyperplasia"] <- "7"

data_d$treat[data_d$`Treatment protocol`=="admitted at CHUK for follow up of suspected multiple myeloma or spinal metastasis"] <- "7"

data_d$treat[data_d$`Treatment protocol`=="His symptoms had begun 2 days prior, with dry cough and asthenia"] <- "1"
data_d$treat[data_d$`Treatment protocol`=="he was operated on 26/06. His condition was complicated by covid status, and he remained on mechanical ventilation until he passed away"] <- "5"

data_d$treat[data_d$`Treatment protocol`=="prepared for transfer to King Faisal Hospital but unfortunately died on the way"] <- "8"


data_d$treat[data_d$`Treatment protocol`=="She was hypoxic on arrival and prepared for transfer"] <- "8"

data_d$treat[data_d$`Treatment protocol`=="he was prepared for transfer to Kaduha DH but died before transfer"] <- "8"

data_d$treat[data_d$`Treatment protocol`=="treated with blood transfusion, resuscitation but passed away"] <- "6"

data_d$treat[data_d$`Treatment protocol`== "He was sent home to be placed in homebased care as he was stable"] <- "-1"

data_d$treat[data_d$`Treatment protocol`== "She was placed in homebased care as she was stable"] <- "-1"


data_d$treat[data_d$`Treatment protocol`== "hypoxic on arrival and treated with antibiotics, favipiravir and oxygen therapy"] <- "2"

data_d$treat[data_d$`Treatment protocol`== "treated but her condition deteriorated, and she passed away"] <- "1"



data_d$treat[data_d$`Treatment protocol`== "He was stable and admitted in HBC. He developed and mild fever and cold, but his condition deteriorated"] <- "-1"

data_d$treat[data_d$`Treatment protocol`== "She was place in homebased care as she was stable"] <- "-1"



data_d$treat[data_d$`Treatment protocol`== "He alerted a CHW and reported weakness and a severe cough. He was prepared for evacuation to Remera Rukoma hospital but passed away"] <- "-1"



data_d$treat[data_d$`Treatment protocol`== "Her family reported that she had been having mild symptoms for a week, until 9th when she developed shortness of breath. She had a sudden cardiac arrest while at home, a post-mortem test at Rubengera HC (Karongi) confirmed covid positive status"] <- "-1"

data_d$treat[data_d$`Treatment protocol`== "antibiotics"] <- "1"

data_d$treat[data_d$`Treatment protocol`== "burn as well as oxygen therapy"] <- "1"

data_d$treat[data_d$`Treatment protocol`== "Home bases care"] <- "-1"

data_d$treat[data_d$`Treatment protocol`== "Tested positive at Kabuga HC (Kamonyi) on 09/08"] <- "1"
data_d$treat[data_d$`Treatment protocol`== "His condition suddenly deteriorated on 17/08 and he passed away at home"] <- "-1"
data_d$treat[data_d$`Treatment protocol`== "placed in home-based care"] <- "-1"
data_d$treat[data_d$`Treatment protocol`== "from home treated with usual protocol"] <- "1"

data_d$treat[data_d$`Treatment protocol`== "He had difficulty breathing, CPR was unsuccessful. Tested positive post-mortem"] <- "1"
data_d$treat[data_d$`Treatment protocol`== "patient died at home and during the assessment  , he was  tested postmortem"] <- "-1"

data_d$treat[data_d$`Treatment protocol`== "Her family reported that she had been having mild symptoms for a week, until 9th when she developed shortness of breath. She had a sudden cardiac arrest while at home, a post-mortem test at Rubengera HC (Karongi) confirmed covid positive status"] <- "-1"

data_d$treat[data_d$`Treatment protocol`== "favirpiravir and oxygen therapy"] <- "2"
data_d$treat[data_d$`Treatment protocol`== "hemodialysis, favipiravir and oxygen therapy"] <- "8"

data_d$treat[data_d$`Treatment protocol`=="oxygen therapy and antibiotics"] <- "1"

data_d$treat[data_d$`Treatment protocol`=="oxygentherapy, antibiotics and favipiravir"] <- "2"

data_d$treat[data_d$`Treatment protocol`=="Treated with oxygen therapy, favipiravir and antibiotics"] <- "2"

data_d$treat[data_d$`Treatment protocol`=="Treated with favipiravir, antibiotics and oxygen therapy"] <- "2"

data_d$treat[data_d$`Treatment protocol`=="treated with antibiotics, favirapiravir and oxygen therapy"] <- "2"

data_d$treat[data_d$`Treatment protocol`== "treated with antibiotics, and oxygen therapy"] <- "2"

data_d$treat[data_d$`Treatment protocol`== "treated with antibiotics, insulin and oxygenotherapy"] <- "2"

data_d$treat[data_d$`Treatment protocol`== "treated with antibiotics, insulin and oxygenotherapy"] <- "2"


data_d$treat[data_d$`Treatment protocol`== "He passed away while in the community on 10/08"] <- "-1"
data_d$treat[data_d$`Treatment protocol`== "Tested positive at Karangara HC (Kamonyi) on 06/08"] <- "-1"
data_d$treat[data_d$`Treatment protocol`== "homebased care"] <- "-1"
data_d$treat[data_d$`Treatment protocol`== "Arrived dead at kanyinya"] <- "-1"
data_d$treat[data_d$`Treatment protocol`== "favirpiravir and oxygen therapy"] <- "2"
data_d$treat[data_d$`Treatment protocol`== "favirpiravir and oxygen therapy"] <- "2"
data_d$treat[data_d$`Treatment protocol`== "hemodialysis, favipiravir and oxygen therapy"] <- "8"

data_d$treat[data_d$`Treatment protocol`== "oxygen therapy and antibiotics"] <- "1"
data_d$treat[data_d$`Treatment protocol`== "oxygen therapy and antibiotics"] <- "1"


data_d$treat[data_d$`Treatment protocol`== "favirpiravir"] <- "2"


data_d$treat[data_d$`Treatment protocol`== "oxygentherapy, antibiotics and favipiravir"] <- "2"
data_d$treat[data_d$`Treatment protocol`== "Treated with oxygen therapy, favipiravir and antibiotics"] <- "2"
data_d$treat[data_d$`Treatment protocol`== "Treated with oxygen therapy, favipiravir and antibiotics"] <- "2"



data_d$treat[data_d$`Treatment protocol`== "Treated with favipiravir, antibiotics and oxygen therapy"] <- "2"


data_d$treat[data_d$`Treatment protocol`== "treated with antibiotics, favirapiravir and oxygen therapy"] <- "2"
data_d$treat[data_d$`Treatment protocol`== "treated with antibiotics, and oxygen therapy"] <- "2"
data_d$treat[data_d$`Treatment protocol`== "treated with antibiotics, insulin therapy and oxygen therapy"] <- "2"

data_d$treat[data_d$`Treatment protocol`== "treated with antibiotics, insulin and oxygenotherapy"] <- "1"


data_d$treat[data_d$`Treatment protocol`== "treated with antibiotics, insulin and oxygenotherapy"] <- "1"



data_d$treat[data_d$`Treatment protocol`== "He passed away while in the community on 10/08"] <- "-1"



data_d$treat[data_d$`Treatment protocol`== "Tested positive at Karangara HC (Kamonyi) on 06/08"] <- "-1"



data_d$treat[data_d$`Treatment protocol`== "homebased care"] <- "-1"
```


```{r,echo=FALSE}

#vaccine
data_d$vacc<-data_d$`Vaccination status`
data_d$vacc[data_d$`Vaccination status`== "No"]<- "0"
data_d$vacc[data_d$`Vaccination status`== "Not vaccinated"]<- "0"
data_d$vacc[data_d$`Vaccination status`== "Unknown"]<- "0"
data_d$vacc[data_d$`Vaccination status`== "Vaccinated"]<- "1"
data_d$vacc[data_d$`Vaccination status`== "Yes"]<- "1"

```

```{r,echo=FALSE}

#type of vaccine

data_d$type_vacc<-data_d$`Vaccine taken`
data_d$type_vacc[data_d$`Vaccine taken`=="1AstraZeneca & 2 Moderna"]<-"1"
data_d$type_vacc[data_d$`Vaccine taken`=="2AstraZeneca & Moderna"]<-"1"
data_d$type_vacc[data_d$`Vaccine taken`=="AstraZeneca & Moderna"]<-"1"
data_d$type_vacc[data_d$`Vaccine taken`=="2Pfizer & Moderna"]<-"2"
data_d$type_vacc[data_d$`Vaccine taken`=="Pfizer & Moderna"]<-"2"
data_d$type_vacc[data_d$`Vaccine taken`=="AstraZeneca, Pfizer & Moderna"]<-"3"
data_d$type_vacc[data_d$`Vaccine taken`=="Moderna"]<-"4"
data_d$type_vacc[data_d$`Vaccine taken`=="AstraZeneca"]<-"5"
data_d$type_vacc[data_d$`Vaccine taken`=="Pfizer"]<-"6"
data_d$type_vacc[data_d$`Vaccine taken`=="Johnson & Johnson"]<-"7"
data_d$type_vacc[data_d$`Vaccine taken`=="Sputnik"]<-"8"
data_d$type_vacc[data_d$`Vaccine taken`=="Sputnik V"]<-"8"

data_d$type_vacc[data_d$`Vaccine taken`=="Sinopharm"]<-"9"
data_d$type_vacc[data_d$`Vaccine taken`=="Not documented"]<-"9"
data_d$type_vacc[data_d$`Vaccine taken`=="Unknown"]<-"10"
data_d$type_vacc[data_d$`Vaccine taken`=="AstraZeneca & Pfizer"]<-"11"
data_d$type_vacc[data_d$`Vaccine taken`=="N/A"]<-NA



```


```{r,echo=FALSE}
# Commodities
#0=No, 1= one comorbidity, 2=pregnant, 3=astma,4=hiv,5=diabetis,7=two comro,8=three and more

data_d$comorb<-data_d$Comorbidity
data_d$comorb[data_d$Comorbidity=="No"| data_d$Comorbidity=="no known comorbidities"|data_d$Comorbidity=="no known cormobidity"| data_d$Comorbidity=="None"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known comorbidity"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known Cormobidities"]<-"0"
data_d$comorb[data_d$Comorbidity=="with no known comorbidities"]<-"0"
data_d$comorb[data_d$Comorbidity=="no existing comorbidities"]<-"0"
data_d$comorb[data_d$Comorbidity=="No information"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known  comorbidity"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known  comorbidity,"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known  comorbiditie"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known  comorbidities."]<-"0"
data_d$comorb[data_d$Comorbidity=="no known comorbiditiesNyarugenge TC"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known comorbidities."]<-"0"
data_d$comorb[data_d$Comorbidity=="no known comorbidity but she was pregnant at 26weeks"]<-"2"

data_d$comorb[data_d$Comorbidity=="unknown history"]<-"0"
data_d$comorb[data_d$Comorbidity=="twin pregnancy at term"]<-"2"



data_d$comorb[data_d$Comorbidity=="no known comorbidity but the patient had undergone a cesarean section"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known comorbidity but with a past medical history use of unknown herbs"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known condition but she was pregnant at 26weeks"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known history"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known history of comorbidity"]<-"0"
data_d$comorb[data_d$Comorbidity=="no known history of comorbidity"]<-"0"
data_d$comorb[data_d$Comorbidity=="with no comorbidity"]<-"0"
data_d$comorb[data_d$Comorbidity=="with no known comorbidity"]<-"0"
data_d$comorb[data_d$Comorbidity=="with no known history"]<-"0"
data_d$comorb[data_d$Comorbidity=="NYIRAKIMONYO Anasthasie"]<-"0"
data_d$comorb[data_d$Comorbidity=="Hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="hemiplegia"]<-"1"
data_d$comorb[data_d$Comorbidity=="hepatic cirrhosis"]<-"1"
data_d$comorb[data_d$Comorbidity=="hepatitis b"]<-"1"
data_d$comorb[data_d$Comorbidity=="hepatitis b and c"]<-"1"
data_d$comorb[data_d$Comorbidity=="hepatitis C"]<-"1"
data_d$comorb[data_d$Comorbidity=="gastric tumor"]<-"1"
data_d$comorb[data_d$Comorbidity=="Gastritis"]<-"1"
data_d$comorb[data_d$Comorbidity=="heart conditions"]<-"1"
data_d$comorb[data_d$Comorbidity=="heart failure"]<-"1"
data_d$comorb[data_d$Comorbidity=="heart failure."]<-"1"
data_d$comorb[data_d$Comorbidity=="heart failure."]<-"1"
data_d$comorb[data_d$Comorbidity=="asthma."]<-"1"
data_d$comorb[data_d$Comorbidity=="bile duct cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="born preterm triplet at 34 weeks"]<-"1"
data_d$comorb[data_d$Comorbidity=="Benign prostate hyperplasia"]<-"1"
data_d$comorb[data_d$Comorbidity=="brain meningioma"]<-"1"
data_d$comorb[data_d$Comorbidity=="Benign prostatic hyperplasia"]<-"1"
data_d$comorb[data_d$Comorbidity=="cardiomyopathy with ischemic stroke"]<-"1"
data_d$comorb[data_d$Comorbidity=="cerebral malaria"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic anemia"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic anemia,"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic gastritis"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="brain tumor"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic immuno-compromising disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease,"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic intestinal obstruction"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic kidney disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic kidney injury"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic malnutrition"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic pulmonary disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic rheumatic arthritis"]<-"1"
data_d$comorb[data_d$Comorbidity=="colon cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="congenital heart disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="dementia"]<-"1"
data_d$comorb[data_d$Comorbidity=="dilated cardiomyopathy"]<-"1"
data_d$comorb[data_d$Comorbidity=="diffuse large B-cell lymphoma,"]<-"1"
data_d$comorb[data_d$Comorbidity=="anemia"]<-"1"
data_d$comorb[data_d$Comorbidity=="asthma"]<-"1"
data_d$comorb[data_d$Comorbidity=="ascites secondary to hepatitis B"]<-"1"
data_d$comorb[data_d$Comorbidity=="acute renal failure"]<-"1"
data_d$comorb[data_d$Comorbidity=="endocarditis"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of  Duodenal cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of  hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of Amyotrophic lateral sclerosis"]<-"1"
data_d$comorb[data_d$Comorbidity=="advanced cervical cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of Alzheimer and femoral  head necrosis"]<-"1"
data_d$comorb[data_d$Comorbidity=="hepatitis c,"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of chronic anemia"]<-"1"
data_d$comorb[data_d$Comorbidity=="History of Ascites  of  unknown origin,"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of blunt abdominal trauma mid-July with laparotomy surgery"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of cardiomyopathy"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of Chronic obstructive  pulmonary disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of chronic obstructive pulmonary disease secondary to heavy smoking"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of chronic obstructive pulmonary disease secondary to heavy smoking"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of convulsions"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of Cryptococcal meningitis"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of DM, HTN and ischemic stroke"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of Esophagus Tumor"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of Pulmonary Tuberculosis"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of lower limb functional impairment"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of decompensated"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of HTN and DM"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of peripartum cardiomyopathy with severe dilated cardiomyopathy"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of Pigeon chest"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of renal failure"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of Sepsis"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of renal failure"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of chronic immunocompromising disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of renal failure"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of stroke secondary to hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of use of traditional medications"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of pleural TB"]<-"1"
data_d$comorb[data_d$Comorbidity=="HTN and AKI"]<-"1"
data_d$comorb[data_d$Comorbidity=="kidney cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of TB-Meningitis,"]<-"1"
data_d$comorb[data_d$Comorbidity=="lower limbs neurological deficits"]<-"1"
data_d$comorb[data_d$Comorbidity=="liver cirrhosis"]<-"1"
data_d$comorb[data_d$Comorbidity=="kidney disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="lung adenocarcinoma"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic asthma"]<-"1"
data_d$comorb[data_d$Comorbidity=="leukemia"]<-"1"
data_d$comorb[data_d$Comorbidity=="immunocompromising disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="lung cancer with possible Diabetes"]<-"1"
data_d$comorb[data_d$Comorbidity=="non-Hodgkin s lymphoma"]<-"1"
data_d$comorb[data_d$Comorbidity=="lung tumor and hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="metabolic syndrome"]<-"1"
data_d$comorb[data_d$Comorbidity=="metastasized gastric cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="lymphoma"]<-"1"
data_d$comorb[data_d$Comorbidity=="Lung fibrosis"]<-"1"
data_d$comorb[data_d$Comorbidity=="mental illness"]<-"1"
data_d$comorb[data_d$Comorbidity=="mouth carcinoma"]<-"1"
data_d$comorb[data_d$Comorbidity=="obesity"]<-"1"
data_d$comorb[data_d$Comorbidity=="dilated cardiomyopathy"]<-"1"
data_d$comorb[data_d$Comorbidity=="peptic  ulcer disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="peptic  ulcer disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="paraplegia secondary to spinal cord injury"]<-"1"
data_d$comorb[data_d$Comorbidity=="paraplegia secondary to spinal cord injury"]<-"1"
data_d$comorb[data_d$Comorbidity=="plasma cell cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="plasma cell cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="paraplegia post trauma."]<-"1"
data_d$comorb[data_d$Comorbidity=="paraplegia post trauma."]<-"1"
data_d$comorb[data_d$Comorbidity=="psychotic disorder"]<-"1"
data_d$comorb[data_d$Comorbidity=="with a history of esophageal cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="pneumonia"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of TB-Meningitis,"]<-"1"
data_d$comorb[data_d$Comorbidity=="nephropathy,"]<-"1"
data_d$comorb[data_d$Comorbidity=="prostate disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="Parkinson s disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="Post C/S peritonitis"]<-"1"
data_d$comorb[data_d$Comorbidity=="preeclampsia"]<-"1"
data_d$comorb[data_d$Comorbidity=="prematurely"]<-"1"
data_d$comorb[data_d$Comorbidity=="prostatic cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="psychosis"]<-"1"
data_d$comorb[data_d$Comorbidity=="schizophrenia."]<-"1"
data_d$comorb[data_d$Comorbidity=="pulmonary TB,"]<-"1"
data_d$comorb[data_d$Comorbidity=="sigmoid cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="pyomyositis"]<-"1"
data_d$comorb[data_d$Comorbidity=="renovascular disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="dysuria"]<-"1"
data_d$comorb[data_d$Comorbidity=="spleen enlargement"]<-"1"
data_d$comorb[data_d$Comorbidity=="spleen enlargement"]<-"1"
data_d$comorb[data_d$Comorbidity=="severe rheumatoid arthritis"]<-"1"
data_d$comorb[data_d$Comorbidity=="severe traumatic brain injury."]<-"1"
data_d$comorb[data_d$Comorbidity=="severe traumatic brain injury."]<-"1"
data_d$comorb[data_d$Comorbidity=="stage 3 cervical cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="Lung cancer"]<-"1"
data_d$comorb[data_d$Comorbidity=="suspicion of a history of congenital heart disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="tuberculosis"]<-"1"
data_d$comorb[data_d$Comorbidity=="uterine prolapse"]<-"1"
data_d$comorb[data_d$Comorbidity=="visual impairment"]<-"1"
data_d$comorb[data_d$Comorbidity=="visual impairment"]<-"1"
data_d$comorb[data_d$Comorbidity=="with history of Hepatitis C"]<-"1"
data_d$comorb[data_d$Comorbidity=="vasculitis"]<-"1"
data_d$comorb[data_d$Comorbidity=="with a history of hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="wasthma"]<-"1"
data_d$comorb[data_d$Comorbidity=="with liver cirrhosis due to Hepatitis C."]<-"1"
data_d$comorb[data_d$Comorbidity=="with liver cirrhosis due to Hepatitis C."]<-"1"
data_d$comorb[data_d$Comorbidity=="w Hepatitis C"]<-"1"
data_d$comorb[data_d$Comorbidity=="stroke and hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity=="stroke and hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity== "history of Asthma and Hepatitis C"]<-"3"
data_d$comorb[data_d$Comorbidity== "history of Asthma and Hepatitis C"]<-"3"
data_d$comorb[data_d$Comorbidity== "HIV acute kidney injury"]<-"4"
data_d$comorb[data_d$Comorbidity== "paraplegic"]<-"1"
data_d$comorb[data_d$Comorbidity== "paraplegic"]<-"1"
data_d$comorb[data_d$Comorbidity== "Hepatitis/Cirrhosis"]<-"1"
data_d$comorb[data_d$Comorbidity== "Hepatic Encephalopathy"]<-"1"
data_d$comorb[data_d$Comorbidity=="Pregnant"]<-"2"
data_d$comorb[data_d$Comorbidity=="pregnancy on 28 weeks and delivered by C-section"]<-"2"
data_d$comorb[data_d$Comorbidity=="pregnant"]<-"2"
data_d$comorb[data_d$Comorbidity=="peritonitis post c-section"]<-"2"
data_d$comorb[data_d$Comorbidity=="post-c section"]<-"2"
data_d$comorb[data_d$Comorbidity=="postpartum"]<-"2"
data_d$comorb[data_d$Comorbidity=="complications post c-section"]<-"2"
data_d$comorb[data_d$Comorbidity=="day 6 post c-section"]<-"2"
data_d$comorb[data_d$Comorbidity=="34 weeks pregnancy"]<-"2"
data_d$comorb[data_d$Comorbidity=="5 days post-partum"]<-"2"
data_d$comorb[data_d$Comorbidity=="Asthma"]<-"3"
data_d$comorb[data_d$Comorbidity=="HIV"]<-"4"
data_d$comorb[data_d$Comorbidity=="HIV, Acute Kidney Injury, and severe sepsis"]<-"4"
data_d$comorb[data_d$Comorbidity=="HIV, Hepatitis B"]<-"4"
data_d$comorb[data_d$Comorbidity=="Hiv,Pulmonary TB,Hepatitis B"]<-"4"
data_d$comorb[data_d$Comorbidity=="Diabete"]<-"5"
data_d$comorb[data_d$Comorbidity=="Diabetes"]<-"5"
data_d$comorb[data_d$Comorbidity=="Diabetes mellitus"]<-"5"
data_d$comorb[data_d$Comorbidity=="diabetic ketoacidosis"]<-"5"
data_d$comorb[data_d$Comorbidity=="history of diabetes"]<-"5"
data_d$comorb[data_d$Comorbidity=="hemiplegia and Diabetes"]<-"5"
data_d$comorb[data_d$Comorbidity=="hemiplegia and Diabetes"]<-"5"
data_d$comorb[data_d$Comorbidity=="diabetic"]<-"5"
data_d$comorb[data_d$Comorbidity=="Admitted with COVID19 on end stage HIV after lost followup from HIV care"]<-"4"
data_d$comorb[data_d$Comorbidity=="hypertension and diabetes"]<-"7"
data_d$comorb[data_d$Comorbidity=="hypertension and renal failure"]<-"7"
data_d$comorb[data_d$Comorbidity=="diabetes and hypertension"]<-"5"
data_d$comorb[data_d$Comorbidity=="diabetes and acute kidney injury"]<-"5"
data_d$comorb[data_d$Comorbidity=="chronic kidney disease and hepatitis C"]<-"7"
data_d$comorb[data_d$Comorbidity=="diabetes and hepatitis c"]<-"7"
data_d$comorb[data_d$Comorbidity=="spinal cord compression and sepsis"]<-"7"
data_d$comorb[data_d$Comorbidity=="sepsis and osteoarthritis"]<-"7"
data_d$comorb[data_d$Comorbidity=="hypertension and asthma"]<-"7"
data_d$comorb[data_d$Comorbidity=="liver cancer and deep vein thrombosis"]<-"7"
data_d$comorb[data_d$Comorbidity=="pregnant and with a history of asthma"]<-"7"
data_d$comorb[data_d$Comorbidity=="diabetes and hypothyroidism"]<-"7"
data_d$comorb[data_d$Comorbidity=="hypertension and cardiomyopathy"]<-"7"
data_d$comorb[data_d$Comorbidity=="hypertension and cardiomyopathy"]<-"7"
data_d$comorb[data_d$Comorbidity=="hypertension and malnutrition"]<-"7"
data_d$comorb[data_d$Comorbidity=="hypertension and malnutrition"]<-"7"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease and chronic kidney disease"]<-"7"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease and tuberculosis"]<-"7"
data_d$comorb[data_d$Comorbidity=="prostate cancer and hypertension"]<-"7"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease and subsequent tuberculosis"]<-"7"
data_d$comorb[data_d$Comorbidity=="diabetes and meningitis"]<-"5"
data_d$comorb[data_d$Comorbidity=="heart disease and diabetes"]<-"7"
data_d$comorb[data_d$Comorbidity=="diabetes and hypertension leading to stroke"]<-"5"
data_d$comorb[data_d$Comorbidity=="hypertension and hepatitis c"]<-"7"
data_d$comorb[data_d$Comorbidity=="hypertension and diabetes as well as right limb amputation"]<-"5"
data_d$comorb[data_d$Comorbidity=="obesity and preeclampsia"]<-"7"
data_d$comorb[data_d$Comorbidity=="hypertension and hepatitis C"]<-"7"
data_d$comorb[data_d$Comorbidity=="2nd degree burns and respiratory distress"]<-"7"
data_d$comorb[data_d$Comorbidity=="hypertension and left hemiplegia"]<-"7"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease and pulmonary tuberculosis"]<-"7"
data_d$comorb[data_d$Comorbidity=="gangrenous foot and heart failure"]<-"7"
data_d$comorb[data_d$Comorbidity=="chronic kidney injury and transplant rejection"]<-"7"
data_d$comorb[data_d$Comorbidity=="chronic kidney injury and transplant rejection"]<-"7"
data_d$comorb[data_d$Comorbidity=="gastric outlet obstruction and acute kidney injury"]<-"7"
data_d$comorb[data_d$Comorbidity=="hypertension asthma and cardiomyopathy"]<-"7"

#More than 2 cormobidities

data_d$comorb[data_d$Comorbidity=="stroke, diabetes, and hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease, cirrhosis, lymphoma, and meningitis"]<-"8"
data_d$comorb[data_d$Comorbidity=="stroke (3 times), hypertension and acute renal failure"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes, hypertension, and heart disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes, hypertension, and heart disease"]<-"8"

data_d$comorb[data_d$Comorbidity=="chronic kidney disease, hypertension, and diabetes"]<-"8"

data_d$comorb[data_d$Comorbidity=="diabetes, hypertension, and kidney disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="enlarged spleen, and liver failure caused by malaria"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension, diabetes, and chronic immunocompromising disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension, diabetes, chronic kidney disease, third degree heart block with pacemaker"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes, hypertension, hepatitis c, cirrhosis and hepatic encelopathy"]<-"8"
data_d$comorb[data_d$Comorbidity=="advanced esophageal carcinoma, chronic kidney disease, diabetes, and hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension, liver cirrhosis and encephalopathy, stroke"]<-"8"
data_d$comorb[data_d$Comorbidity=="pulmonary embolism with right heart dilation and atrial fibrillation"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes, hypertension, and chronic kidney disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="hepatitis, chronic kidney disease, hypertension, and diabetes"]<-"8"

data_d$comorb[data_d$Comorbidity=="chronic kidney disease, chronic immunocompromising disease, hypertension, and congestive heart failure"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease, hypertension, and diabetes"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes, hypertension, renal failure, lower limb gangrene and malnutrition"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease, tuberculosis and cryptococcal meningitis"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes, hypertension, chronic gastritis"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes, hypertension, and stroke"]<-"8"
data_d$comorb[data_d$Comorbidity=="history of cute kidney injury, chronic kidney disease and diabetes"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes, hypertension, and chronic kidney disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="cardiomyopathy, acute kidney injury and pre-eclampsia"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension chronic kidney disease and hypertension cardiomyopathy"]<-"8"
data_d$comorb[data_d$Comorbidity=="Diabetes, hypertension, and obesity"]<-"8"
data_d$comorb[data_d$Comorbidity=="Acute Cerebelitis ,Mild global cortical atrophy and lacunar infarct as confirmed by  head CT"]<-"8"
data_d$comorb[data_d$Comorbidity=="acute kidney and liver injury chronic Anemia"]<-"8"
 data_d$comorb[data_d$Comorbidity=="acute kidney injury and acute lung injury"]<-"8"
 data_d$comorb[data_d$Comorbidity=="Acute Kidney Injury and Liver Injury"]<-"8"
 data_d$comorb[data_d$Comorbidity=="acute liver and kidney injury paralysis"]<-"8"
 data_d$comorb[data_d$Comorbidity=="Hepatitis B&C,chronic liver disease and malnutrition"]<-"8"
 data_d$comorb[data_d$Comorbidity=="diabetes type1 ,hypertension,chronic kidney disease"]<-"8"
 data_d$comorb[data_d$Comorbidity=="Asthma and Heart failure"]<-"8"
data_d$comorb[data_d$Comorbidity=="asthma and hepatitis c"]<-"8"
data_d$comorb[data_d$Comorbidity=="asthma and hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity=="Alzheimer and senile dementia"]<-"8"
data_d$comorb[data_d$Comorbidity=="amenorrhea, 3 previous uterine scars"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease and anemia"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease and cardiomyopathy"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease and epilepsy"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease and hepatitis c"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease and hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic kidney disease and Benign prostate hyperplasia"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic kidney disease and hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic obstructive pulmonary disease and renovascular disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic obstructive pulmonary disease and renovascular disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="Diabetes and Acute Kidney Injury"]<-"8"
data_d$comorb[data_d$Comorbidity=="Diabetes and Acute Kidney Injury"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes and Acute kidney injury"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes and cardiomyopathy"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes and cerebral malaria"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes and chronic immunocompromising disease,"]<-"8"
data_d$comorb[data_d$Comorbidity=="Diabetes and Chronic Kidney Disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="Diabetes and Hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes and obesity (BMI over 40)"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes and obesity,"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes hypertension and acute kidney injury"]<-"8"
data_d$comorb[data_d$Comorbidity=="down syndrome and congestive heart failure"]<-"8"
data_d$comorb[data_d$Comorbidity=="down syndrome and heart failure"]<-"8"
data_d$comorb[data_d$Comorbidity=="heart failure and hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity=="heart failure and kidney injury"]<-"8"
data_d$comorb[data_d$Comorbidity=="Heart failure on pericarditis"]<-"8"
data_d$comorb[data_d$Comorbidity=="hepatitis C and  Hepatitis B"]<-"8"
data_d$comorb[data_d$Comorbidity=="Hepatitis C and  Liver cirrhosis"]<-"8"
data_d$comorb[data_d$Comorbidity=="Hepatitis C and chronic liver disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="Hepatitis C and Cirrhosis"]<-"8"
data_d$comorb[data_d$Comorbidity=="hepatitis c and hepatocarcinoma"]<-"8"
data_d$comorb[data_d$Comorbidity=="history of Asthma and mental disorder"]<-"8"
data_d$comorb[data_d$Comorbidity=="history of HBV and heapatic Encephalopathy"]<-"8"
data_d$comorb[data_d$Comorbidity=="history of HIV ,and Chronic kidney disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="history of HIV, asthma and Obesity"]<-"8"
data_d$comorb[data_d$Comorbidity=="history of Hypertension and ischemic stroke"]<-"8"
data_d$comorb[data_d$Comorbidity=="history of Hypothyroidism and Hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity=="history of Kidney failure and diabetes"]<-"8"
data_d$comorb[data_d$Comorbidity=="HIV  and Tuberculosis with poor drug adherence"]<-"8"
data_d$comorb[data_d$Comorbidity=="HIV ,severe malnutrition,and tuberculosis"]<-"8"
data_d$comorb[data_d$Comorbidity=="HIV and hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity=="HIV and suspicion of lymphoma"]<-"8"
data_d$comorb[data_d$Comorbidity=="HIV and tuberculosis"]<-"8"
data_d$comorb[data_d$Comorbidity=="HIV and TB"]<-"8"
data_d$comorb[data_d$Comorbidity=="history of being newly diagnosed with HIV"]<-"8"
data_d$comorb[data_d$Comorbidity=="Hypertension and  HIV"]<-"8"
data_d$comorb[data_d$Comorbidity=="Hypertension and Anemia"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and chronic gastritis"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and chronic kidney disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and Diabetes"]<-"8"
data_d$comorb[data_d$Comorbidity=="Hypertension and Diabetes"]<-"8"
data_d$comorb[data_d$Comorbidity=="Hypertension and Diabetes mellitus"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and end stage congestive heart failure"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and femur fracture"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and gastritis"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and gout"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and heart block"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and hemiplegia"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and hemiplegia post stroke"]<-"8"
data_d$comorb[data_d$Comorbidity=="Hypertension and Hepatitis C"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and myocardial infarction"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension and stroke"]<-"8"
data_d$comorb[data_d$Comorbidity=="Hypertension and Stroke with left hemiplegia"]<-"8"

data_d$comorb[data_d$Comorbidity=="Hypertension and Stroke with left hemiplegia"]<-"8"

data_d$comorb[data_d$Comorbidity=="hypertension, chronic kidney disease and diabetes"]<-"8"

data_d$comorb[data_d$Comorbidity=="immunocompromising disease and malnutrition 
"]<-"8"
data_d$comorb[data_d$Comorbidity=="Ischemic stroke, Chronic Kidney Disease
"]<-"8"

data_d$comorb[data_d$Comorbidity=="hypertension, diabetes, and schizophrenia
"]<-"8"

data_d$comorb[data_d$Comorbidity=="intestinal obstruction and 26-week pregnancy"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension, diabetes, end stage renal disease"]<-"8" 

data_d$comorb[data_d$Comorbidity=="ischemic stroke, hepatitis c"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension, diabetes, end stage renal disease"]<-"8"

data_d$comorb[data_d$Comorbidity=="hypertension,history of stroke and unhealed fractures."]<-"8"

data_d$comorb[data_d$Comorbidity=="Hypertension ,chronic kidney  disease , Hepatitis C and chronic liver disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="Hypertension ,diabetes,Asthma and hepatitis c"]<-"8"

data_d$comorb[data_d$Comorbidity=="Hypertension , Diabetes mellitus , tuberculosis  (treated) and prostatic adenoma"]<-"8"

data_d$comorb[data_d$Comorbidity=="Hypertension , Diabetes mellitus , tuberculosis  (treated) and prostatic adenoma"]<-"8"

data_d$comorb[data_d$Comorbidity=="chronic immunocompromising disease, syphilis, splenomegaly stage II with anemia"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic obstructive pulmonary disease, cirrhosis, and chronic kidney disease"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic obstructive pulmonary disease, cirrhosis, and chronic kidney disease"]<-"8"

data_d$comorb[data_d$Comorbidity=="down syndrome, cardiomyopathy and thrombocytopenia"]<-"8"

data_d$comorb[data_d$Comorbidity=="espiratory distress, and decreased level of consciousness."]<-"8"

data_d$comorb[data_d$Comorbidity=="gastrointestinal bleeding, anemia, vascular dementia"]<-"8"

data_d$comorb[data_d$Comorbidity=="history of Asthma , Chronic kidney disease and hemiparesis"]<-"8"

data_d$comorb[data_d$Comorbidity=="history of chronic kidney disease, hypertension, hepatorenal syndrome, Anemia, and congestive heart failure"]<-"8"


data_d$comorb[data_d$Comorbidity=="history of Blunt chest trauma with hemothorax, stroke and congestive heart failure"]<-"8"

data_d$comorb[data_d$Comorbidity=="history of Diabetes mellitus, Hypertension and chronic obstructive pulmonary disease"]<-"8"

data_d$comorb[data_d$Comorbidity=="history of Hypertension , diabetes Mellitus and  asthma"]<-"8"

data_d$comorb[data_d$Comorbidity=="history of diabetes and Hypertension"]<-"8"

data_d$comorb[data_d$Comorbidity=="history of Diabetes and Mental disorder"]<-"8"

data_d$comorb[data_d$Comorbidity=="hypertension Chronic Kidney disease and venous insufficiency"]<-"8"

data_d$comorb[data_d$Comorbidity=="hypertension hepatitis C and cirrhosis"]<-"8"

data_d$comorb[data_d$Comorbidity=="hypertension and tension pneumothora"]<-"8"

data_d$comorb[data_d$Comorbidity=="renovascular disease, systolic anterior motion, and anemia"]<-"8"

data_d$comorb[data_d$Comorbidity=="splenectomy, diabetes, and hypertension"]<-"8"

data_d$comorb[data_d$Comorbidity=="pneumonia and chronic renal failure"]<-"8"

data_d$comorb[data_d$Comorbidity=="obstructive sleep apnea hypertrophic tonsils and adenoids"]<-"8"

data_d$comorb[data_d$Comorbidity=="asthma, silicosis, and tuberculosis"]<-"8"
data_d$comorb[data_d$Comorbidity=="gout and hypertension"]<-"8"
data_d$comorb[data_d$Comorbidity=="chronic aphasia and falsy palsy"]<-"8"
data_d$comorb[data_d$Comorbidity=="immunocompromising disease and malnutrition"]<-"8"


data_d$comorb[data_d$Comorbidity=="diabetes"]<-"8"
data_d$comorb[data_d$Comorbidity=="Parkinson s disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of TB-Meningitis"]<-"1"
data_d$comorb[data_d$Comorbidity=="History of Ascites  of  unknown origin"]<-"1"

data_d$comorb[data_d$Comorbidity=="history of Cirrhosis with portal hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="no known Comorbidity"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of cirrhosis"]<-"1"

data_d$comorb[data_d$Comorbidity=="history of cirrhosis"]<-"1"

data_d$comorb[data_d$Comorbidity=="Hepatitis/Cirrhosis, Hepatic Encephalopathy"]<-"1"

data_d$comorb[data_d$Comorbidity=="HTN"]<-"1"

data_d$comorb[data_d$Comorbidity=="hypertension, diabetes"]<-"8"
data_d$comorb[data_d$Comorbidity=="Hepatitis/Cirrhosis, Hepatic Encephalopathy"]<-"8"
data_d$comorb[data_d$Comorbidity=="hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="Hepatitis B"]<-"1"

data_d$comorb[data_d$Comorbidity=="unknown history"]<-"0"
data_d$comorb[data_d$Comorbidity=="Hepatitis C"]<-"1"
data_d$comorb[data_d$Comorbidity=="diabetes and chronic immunocompromising disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="diffuse large B-cell lymphoma"]<-"1"
data_d$comorb[data_d$Comorbidity=="peritonitis"]<-"1"
data_d$comorb[data_d$Comorbidity=="nephropathy"]<-"1"
data_d$comorb[data_d$Comorbidity=="ic immunocompromising disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="non-Hodgkin s lymphoma"]<-"1"
data_d$comorb[data_d$Comorbidity=="undiagnosed diabetes"]<-"1"
data_d$comorb[data_d$Comorbidity=="hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="no known comorbiditie"]<-"0"

data_d$comorb[data_d$Comorbidity=="twin pregnancy at term"]<-"2"
data_d$comorb[data_d$Comorbidity=="hypertension, diabetes, and schizophrenia"]<-"2"
data_d$comorb[data_d$Comorbidity=="epilepsy"]<-"1"
data_d$comorb[data_d$Comorbidity=="pulmonary tuberculosis"]<-"1"
data_d$comorb[data_d$Comorbidity=="Ischemic stroke, Chronic Kidney Disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of Hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of Cirrhosis with portal hypertension"]<-"1"

data_d$comorb[data_d$Comorbidity=="Asthma and hepatitis"]<-"1"
data_d$comorb[data_d$Comorbidity=="chronic Kidney disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="diabetes and Hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="paraplegia"]<-"1"
data_d$comorb[data_d$Comorbidity=="Ischemic stroke, Chronic Kidney Disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="suspected diabetes"]<-"5"
data_d$comorb[data_d$Comorbidity=="suspected diabetes"]<-"5"
data_d$comorb[data_d$Comorbidity=="stroke"]<-"1"
data_d$comorb[data_d$Comorbidity=="HTN and DM"]<-"8"
data_d$comorb[data_d$Comorbidity=="history of DM"]<-"1"
data_d$comorb[data_d$Comorbidity=="history of Hypertension"]<-"1"
data_d$comorb[data_d$Comorbidity=="diabetes and obesity"]<-"5"
data_d$comorb[data_d$Comorbidity=="Asthma and hepatitis C"]<-"8"
data_d$comorb[data_d$Comorbidity=="diabetes and chronic kidney disease"]<-"5"
data_d$comorb[data_d$Comorbidity=="hypertension , Diabetes mellitus"]<-"5"
data_d$comorb[data_d$Comorbidity=="non-Hodgkin’s lymphoma"]<-"5"
data_d$comorb[data_d$Comorbidity=="hepatitis"]<-"5"
data_d$comorb[data_d$Comorbidity=="hypertension."]<-"1"
data_d$comorb[data_d$Comorbidity=="pulmonary TB"]<-"1"
data_d$comorb[data_d$Comorbidity=="Parkinson’s disease"]<-"1"
data_d$comorb[data_d$Comorbidity=="hepatitis B"]<-"1"
data_d$comorb[data_d$Comorbidity=="hepatitis c"]<-"1"
data_d$comorb[data_d$Comorbidity=="Parkinson’s"]<-"1"

```

```{r,echo=FALSE}

data_d$days<- abs(difftime(data_d$`Date of death`, data_d$`Admission date`,units = "days"))
  


```

```{r,echo=FALSE}

write.csv(data_d,file = "data_d1.csv")

```

## Introduction

## Methods

## Results


 ----------------------------------------------------------
| Characteristics                       | n        | %    | 
|---------------------------------------|----------|------|
| COVID-19 Deaths                       |          |      |
|---------------------------------------|----------|------|  
| Alive                                 | 876      | 41.6 |  
| Died                                  | 1,228    | 58.4 |  
| Total                                 | 2,1047   | 100  |
|---------------------------------------|----------|------|
| Gender                                |          |      |
|---------------------------------------|----------|------|
| Female                                | 1,107    | 52.6 |  
| Males                                 | 997      | 47.4 |
| Total                                 | 2,104    | 100  | 
|---------------------------------------|----------|------|
|Age group                              |          |      |
|---------------------------------------|----------|------|
| <20 Years                             | 50       | 2.4  |  
| 20-30 Years                           | 142      | 6.7  |  
| 30-40 Years                           | 279      | 13.3 |    
| 40-50 Years                           | 261      | 12.4 |   
| 50-60 Years                           | 267      | 12.7 |   
| 60-70 Years                           | 383      | 18.2 | 
| 70-80 Years                           | 346      | 16.4 |  
| 80+ Years                             | 376      | 17.9 | 
| Total                                 | 2,104    | 100  |
|---------------------------------------|----------|------|
| Treatment                             |          |      |
|---------------------------------------|----------|------|
| No medecine                           | 116      | 5.5  |  
| FVP/IVM/O2/ABT                        | 1,904    | 90.5 |  
| MAB/Cocktail                          | 84       | 4    |   
| Total                                 | 2,104    | 100  |
|---------------------------------------|----------|------|
| Vaccination                           |          |      |
|---------------------------------------|----------|------|
| Not vaccineted                        | 1,892    | 89.9 |  
|  Vaccineted                           | 212      | 10.1 |  
| Total                                 | 2,104    | 100  |  
| Type of Vaccine                       |          |      |  
| AstraZeneca & Moderna                 | 5        | 0.2  |   
| Pfizer & Moderna                      | 72       | 3.4  |   
| AstraZeneca, Pfizer & Moderna         | 1        | 0    |   
| Moderna                               | 1        | 0    |   
| AstraZeneca                           | 76       | 3.6  |   
| Pfizer                                | 82       | 3.9  |   
| Johnson & Johnson                     | 3        | 0.1  |  
| Sputnik                               | 1        | 0    |   
| Sinopharm                             | 4        | 0.2  |   
| AstraZeneca & Pfizer                  | 1        | 0    |   
| Not information                       | 1,858    | 88.3 |  
| Total                                 | 2,104    | 100  |
|---------------------------------------|----------|------|
| Doses                                 |          |      |
|---------------------------------------|----------|------|
| No dose                               | 1,858    | 88.3 |   
| First dose                            | 156      | 7.4  |   
| Second dose                           | 79       | 3.8  |   
| Buster dose                           | 11       | 0.5  |   
| Total                                 | 2,104    | 100  |
|---------------------------------------|----------|------|
| Cormobidities                         |          |      |
|---------------------------------------|----------|------|
|  No   Comorbity                       | 1,168    | 55.5 |  
|  One comorbity                        | 424      | 20.2 |  
| Pregnant women                        | 90       | 4.3  |   
| Asthma                                | 29       | 1.4  |   
| HIV Positive                          | 48       | 2.3  |   
| Diabetes                              | 82       | 3.9  |   
| Two comorbities                       | 53       | 2.5  |   
| Three and More comorbidities          | 210      | 10   |   
| Total                                 | 2,104    | 100  |
|---------------------------------------|----------|------|
| Length of stay in treatment   centers |          |      |
|---------------------------------------|----------|------|
| 0-14 Days                             | 836      | 39.7 |   
| 15-29 Days                            | 327      | 15.5 |   
| 30 Days +                             | 941      | 44.7 |   
| Total                                 | 2,104    | 100  |
|----------------------------------------------------------

### Data exploration
```{r  echo=FALSE}

```

